Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-08 manuscript/paper-tycho.tex
B-damping debug, fits; cull Kepler regs
Testing/debugging B-damping calculations manually
Set up preliminary fits to explore parameter space
Cull Kepler regions-3 and run through pipeline

% Further work -- radio
As has been noted by many workers, observations of radio synchrotron rims would
provide strong and immediate evidence for magnetic field damping (at the
lengthscales of said radio rims).  Previous workers have certainly tried
\citep{cassam-chenai2007, morlino2012} but it seems not easy.
A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
Williams) will offer a rich dataset of sub-arcsecond observations that may
reveal more about rim morphology and perhaps even temporal variation over a 10+
year baseline.

@@

%\clearpage

% ========
% Appendix
% ========
%\appendix
%
%\setcounter{table}{0}
%\renewcommand{\thetable}{A\arabic{table}}
%\setcounter{figure}{0}
%\renewcommand{\thefigure}{A\arabic{figure}}

>>>>

% Further work -- radio
As has been noted by many workers, observations of radio synchrotron rims would
provide strong and immediate evidence for magnetic field damping (at the
lengthscales of said radio rims).  Previous workers have certainly tried
\citep{cassam-chenai2007, morlino2012} but it seems not easy.
A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
Williams) will offer a rich dataset of sub-arcsecond observations that may
reveal more about rim morphology and perhaps even temporal variation over a 10+
year baseline (compare to \citet{katsuda2010-sn1006}).

@@

% ========
% Appendix
% ========
\clearpage
\appendix

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\section{Derivation for synchrotron roll-off and diffusion}

% This is NOT optimized for 2-column layout

Assume that a DSA model explains the observed e-/synchrotron spectra
cut-off/roll-off.  We estimate e- cut-off energy by equating
$\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
\[
    \frac{3r}{r-1} \frac{r D_d + D_u}{v_s^2} = \frac{1}{b B^2 \Ecut}
\]
(\emph{I don't know if this equality was designed to exactly obtain the electron
cutoff energy, or is just a rough/scaling relation -- pull up Drury (1983) to
check this})
Following through the arguments/assumptions in Parizot et al. (2006) yields
(using $13.3 \unit{erg} = 8.3 \unit{TeV}$):
\[
    \Ecut =
        \left( 13.3 \unit{erg} \right)^{\frac{2}{1+\mu}}
        \left( \frac{B_0}{100 \muG} \right)^{-\frac{1}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm\;s^{-1}}} \right)^{\frac{2}{1+\mu}}
        \eta^{-\frac{1}{1+\mu}}
\]
Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
invoking the delta function assumption $\nu_{\mt{cut}} = c_m \Ecut^2 B$ with
$c_m = 1.822 \times 10^{18}$.
(\emph{Again, I don't know if this is an equality or just a scaling.  We'd need
to relate the electron spectrum cut-off to the derived synchrotron spectrum
cut-off, as is done (I think) by Zirakashvili and Aharonian (2007).})
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \eta^{-\frac{2}{1+\mu}}
\]
In the case of $\mu = 1$ this yields:
\[
    \nu_{\mt{cut}} = (0.133 \unit{keV} / h)
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{2}
        \eta^{-1}
\]
For $\mu \neq 1$ this is no longer independent of magnetic field.  But,
there is hope.  Rewrite this in terms of $\eta_2$ using
$\eta = \eta_2 E_2^{1-\mu}$ and write:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( E_2 \right)^{-\frac{2(1-\mu)}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
With $E_2 = \left( (2 \unit{keV}/h) / (c_m B) \right)^{1/2}$, or
$E_2 = \left( 0.2657 \unit{erg^2\;G} / B \right)^{1/2}$, we obtain:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( \frac{0.2657 \unit{erg^2\;G}}{B} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
And, the magnetic field terms cancel!  Hey presto.
Our final usable result is:
\[
    \nu_{\mt{cut}} = c_m
        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
        \left( 0.2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
        \left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
\]
